Presentation Title

### 2017-08-27 paper/s4-analysis.tex
Fix paper
Grammar fixes etc.

\section{Correctness and Fault Tolerance Analysis}
\label{sec:analysis}
We evaluate our system analytically to ensure the desired properties (\Cref{def:consensus} and \Cref{def:validation}) hold.
An informal argument is given in this section, we refer to~\cite[Chapter 4]{checo}??? for an in-depth analysis.

\subsection{Correctness of the Consensus Protocol}
Recall that the consensus protocol properties (\Cref{def:consensus}) has
four items---agreement, validity, termination and fairness.
The first three hold due to the following facts.
\begin{itemize}
    \item The CP blocks sent to the facilitators are eventually delivered and then ACS eventually starts.
    \item Agreement, validity and termination hold for ACS as they are the properties of ACS and are proven to hold in~\cite{miller2016honey}.
    \item The consensus result and signatures are eventually disseminated to all the nodes,
        so honest nodes must hold the same result as the honest facilitators.
\end{itemize}

Fairness holds because we model $\textsf{H}(\cdot)$ as a query to the random oracle.
Sorting nodes by the luck value $\textsf{H}(\C || pk)$ can be seen as a random permutation of a list of nodes.
Therefore every node has the same probability of becoming a facilitator.

\subsection{Correctness of the Validation Protocol}
\label{sec:correctness-of-validity}
Using the previous result,
we show that the agreement and validity properties (from~\Cref{def:validation}) hold for the validation protocol.

The validity property holds because we use $\textsf{get\_validity}(\cdot)$ in the validation protocol.
The agreement property holds because we model $\textsf{H}(\cdot)$ as a query to a random oracle.
Suppose two honest nodes decided on two different states, \emph{valid} and \emph{invalid} for the same transaction.
For that to happen, two agreed fragments must exist for the same transaction,
but these fragments must also have the same agreed enclosure.
Recall that blocks form a hash chain.
So this is not possible unless the adversary can compute the inverse of $\textsf{H}(\cdot)$ with high probability.

Liveness, unfortunately, does not hold in our model.
A malicious node can act honestly when running the transaction protocol,
but then never respond to any validation requests.
Therefore there are transactions that can never be validated.
Nevertheless, the malicious node will be at an economic loss if it is not responsive because honest nodes are less likely to make contact with nodes that do not respond to validation requests.

A stronger version of the validity definition exists.
That is, if two honest nodes make a transaction,
then the transaction state is always valid in addition to our current validity definition.
Under our purely asynchronous model, we cannot guarantee this stronger version.
Since the adversary can delay any message for any amount of time,
it can make sure all \texttt{tx\_req} messages are delivered in a round later than the round which the message is sent.
Effectively, the transaction pair would always be in different rounds and the validation protocol would not output \emph{valid}.
We believe in a relaxed model, i.e. a weakly synchronous model, a stronger validity definition is possible.

\subsection{Fault Tolerance}
Finally, we consider the effect when the number of adversaries is more than $t$.
This is useful because in practice it is difficult to guarantee that $t$ satisfies $n \ge 3t + 1$,
especially when $N$ is large.
Hence we are interested in the probability for this to happen under our facilitator election process.
The problem is modelled by a hypergeometric distribution,
where the random variable $X$ is the number of malicious nodes.
For our system to fail, we are interested in the following probability.
$$
\Pr[X \ge \lfloor \frac{n-1}{3} \rfloor + 1]
$$
Let $E[X] = n\alpha$ where $0 \le \alpha \le \lfloor \frac{n-1}{3} \rfloor/n$.
Using the tail inequality found in~\cite{skala2013hypergeometric}
$$
\Pr[X \ge E[X] + \tau n] \le e^{-2\tau^2n},
$$
and setting 
$$
\tau = \frac{\lfloor \frac{n-1}{3} \rfloor + 1}{n} - \alpha,
$$
we arrive at the following bound
$$
\Pr[X \ge \lfloor \frac{n-1}{3} \rfloor + 1] \le e^{-2 \big(\frac{\lfloor  \frac{n - 1}{3} \rfloor + 1}{n} - \alpha \big)^2 n}.
$$

The bound is not tight, but it is useful for picking parameters for the desired level of fault tolerance.
If $n$ is known, then we can pick a $\alpha$ such that the probability becomes small.
On the other hand, if $\alpha$ is fixed, we may increase $n$ to achieve the same.
Furthermore, hypergeometric distributions have light tails with ``faster-than-exponential fall-off''~\cite{skala2013hypergeometric}.
So the probability of picking more than $\lfloor \frac{n-1}{3} \rfloor$ malicious nodes drops of exponentially as the expected value moves away from $\lfloor \frac{n-1}{3} \rfloor$.
To put this into perspective,
suppose $n = 1000$ and $\alpha = 1/5$, i.e. a fifth of the nodes are malicious.
Then the probability to elect more malicious nodes than the threshold is only $2.6 \times 10^{-16}$.

>>>>

\section{Correctness and Fault Tolerance Analysis}
\label{sec:analysis}
We evaluate our system analytically to ensure the desired properties (\Cref{def:consensus} and \Cref{def:validation}) hold.
An informal argument is given in this section.
We refer to~\cite[Chapter 4]{checo} for an in-depth analysis.

\subsection{Correctness of the Consensus Protocol}
$\Pi_c$ correctly implements the \textsc{Checo} consensus protocol (\Cref{def:consensus}) due to the following.
The agreement, validity and termination properties hold because:
\begin{itemize}
    \item The CP blocks sent to the facilitators are eventually delivered, and then ACS eventually starts.
    \item Agreement, validity and termination hold for ACS as they are the properties of ACS and are proven to hold in~\cite{miller2016honey}.
    \item The consensus result and signatures are eventually disseminated to all the nodes,
        so honest nodes must hold the same result as the honest facilitators.
\end{itemize}
Fairness holds because we model $\textsf{H}(\cdot)$ as a query to the random oracle.
Sorting nodes by the luck value $\textsf{H}(\C || pk)$ can be seen as a random permutation of a list of nodes.
Therefore every node with a CP block in the consensus result has the same probability of becoming a facilitator.

\subsection{Correctness of the Validation Protocol}
\label{sec:correctness-of-validity}
Using the previous result,
we show that $\Pi_v$ implements the agreement and validity properties of a \textsc{Checo} validation protocol (\Cref{def:validation}).

The validity property holds because we use $\textsf{get\_validity}(\cdot)$ in the validation protocol.
The agreement property holds because we model $\textsf{H}(\cdot)$ as a query to a random oracle.
That is, suppose two honest nodes decided on two different states, \emph{valid} and \emph{invalid} for the same transaction.
For that to happen, two agreed fragments must exist for the same transaction,
but these fragments must also have the same agreed enclosure.
Recall that blocks form a hash chain.
So this is not possible unless the adversary can compute the inverse of $\textsf{H}(\cdot)$ with high probability.

Liveness, unfortunately, does not hold in our model.
A malicious node can act honestly when running the transaction protocol,
but then never respond to any validation requests.
Therefore some transactions can never be validated.
Nevertheless, the malicious node will be at an economic loss if it is not responsive because honest nodes are less likely to make contact with nodes that do not respond to validation requests.
If the probabilistic fork detection proposal (\Cref{sec:fork}) is used,
the uncooperative nodes will have more incentive to participate in the protocol.

% A stronger version of the validity definition exists.
% That is, if two honest nodes make a transaction,
% then the transaction state is always valid in addition to our current validity definition.
% Under our purely asynchronous model, we cannot guarantee this stronger version.
% Since the adversary can delay any message for any amount of time,
% it can make sure all \texttt{tx\_req} messages are delivered in a round later than the round which the message is sent.
% Effectively, the transaction pair would always be in different rounds and the validation protocol would not output \emph{valid}.
% We believe in a relaxed model, i.e. a weakly synchronous model, a stronger validity definition is possible.

\subsection{Fault Tolerance}
Finally, we consider the effect when the number of adversaries is more than $t$,
which is useful because in practice it is difficult to guarantee that $t$ satisfies $n \ge 3t + 1$,
especially when $N$ is large.
Hence we are interested in the probability for this to happen under our facilitator election process.
The problem is modelled by a hypergeometric distribution,
where the random variable $X$ is the number of malicious nodes.
For our system to fail, we are interested in the following probability.
$$
\Pr[X \ge \lfloor \frac{n-1}{3} \rfloor + 1]
$$
Let $E[X] = n\alpha$ where $0 \le \alpha \le \lfloor \frac{n-1}{3} \rfloor/n$.
Using the tail inequality found in~\cite{skala2013hypergeometric}
$$
\Pr[X \ge E[X] + \tau n] \le e^{-2\tau^2n},
$$
and setting 
$$
\tau = \frac{\lfloor \frac{n-1}{3} \rfloor + 1}{n} - \alpha,
$$
we arrive at the following bound
$$
\Pr[X \ge \lfloor \frac{n-1}{3} \rfloor + 1] \le e^{-2 \big(\frac{\lfloor  \frac{n - 1}{3} \rfloor + 1}{n} - \alpha \big)^2 n}.
$$

The bound is not tight, but it is useful for picking parameters for the desired level of fault tolerance.
If $n$ is known, then we can pick a $\alpha$ such that the probability becomes small.
On the other hand, if $\alpha$ is fixed, we may increase $n$ to achieve the same.
Furthermore, hypergeometric distributions have light tails with ``faster-than-exponential fall-off''~\cite{skala2013hypergeometric}.
So the probability of picking more than $\lfloor \frac{n-1}{3} \rfloor$ malicious nodes drops off exponentially as the expected value moves away from $\lfloor \frac{n-1}{3} \rfloor$.
To put this into perspective,
suppose $n = 100$ and $\alpha = 1/10$, i.e. 10\% of the nodes are malicious,
then the probability to elect more malicious nodes than the threshold is $9.9 \times 10^{-6}$.
% To put this into perspective,
% suppose $n = 1000$ and $\alpha = 1/5$, i.e. a fifth of the nodes are malicious.
% Then the probability to elect more malicious nodes than the threshold is only $2.6 \times 10^{-16}$.

### 2017-08-27 paper/s5-evaluation.tex
Grammar fixes etc.

The global throughput results are shown in~\Cref{fig:global-throughput}.
We consider~\Cref{fig:global-throughput-fixed} as the ideal case,
where nodes only make transactions with a fixed node.
We consider \Cref{fig:global-throughput-random} as the worst case,
where nodes make transactions with random nodes and the caching mechanism is unlikely to be used.
Observe that the transaction rate is much lower in~\Cref{fig:global-throughput-random}.
This is because the communication of an agreed fragment is necessary to verify every transaction (no caching),
putting a strain on our network infrastructure.
In practice, we do not expect such behaviour to occur as it is possible to cache agreed fragments.

For~\Cref{fig:global-throughput-fixed},
the magnitude of our throughput may not be self-evident at first glance.
Recall that we fixed the transaction rate to 2 TPS,
but how is it possible to have around 4800 transactions per second for 1200 nodes (which is 4 TX/s)?
This is due to the way validated transactions are calculated.
Transactions are between two parties, hence if every node makes two transactions per second,
every node also expects to receive two transactions per second.
Hence, for every node, the TX blocks are created at 4 per second.
Validation requests are sent at the same rate, which explains the magnitude.
Overall, the throughput has a linear relationship with the population size.
This result is a strong indication of the horizontal scalability which we aimed to achieve.

The communication complexity of the consensus protocol grows polynomially as the number of facilitators grows linearly.
Hence, the consensus protocol will take longer to complete and larger fragments must be sent for transaction verification.
The result is that transactions verification will take longer.
On the other hand, it does not significantly impact the throughput.
We refer the reader to~\cite[Chapter 5]{checo} for additional analysis of the effect of the number of facilitators as well as other experimental results.

>>>>

The global throughput results are shown in~\Cref{fig:global-throughput}.
We consider~\Cref{fig:global-throughput-fixed} as the ideal case,
where nodes only make transactions with a fixed node.
\Cref{fig:global-throughput-random} is the worst case,
where nodes make transactions with random nodes and the caching mechanism is unlikely to be used.
Observe that the transaction rate is much lower in~\Cref{fig:global-throughput-random},
which is because the communication of an agreed fragment is necessary to verify every transaction (no caching),
putting a strain on our network infrastructure.
% In practice, we do not expect such behaviour to occur as it is possible to cache agreed fragments.

For~\Cref{fig:global-throughput-fixed},
the magnitude of our throughput may not be self-evident at first glance.
Recall that we fixed the transaction rate to 2 TPS,
but how is it possible to have around 4800 transactions per second for 1200 nodes (which is 4 TPS)?
It is due to the way validated transactions are calculated.
Transactions are between two parties, hence if every node makes two transactions per second,
every node also expects to receive two transactions per second.
Hence, for every node, the TX blocks are created at 4 per second.
Validation requests are sent at the same rate, which explains the magnitude.
Overall, the throughput has a linear relationship with the population size.
This result is a strong indication of the horizontal scalability which we aimed to achieve.

The downside of our design is that the communication complexity of the consensus protocol grows polynomially as the number of facilitators grows linearly.
Hence, the consensus protocol will take longer to complete, and larger fragments must be sent for transaction verification.
On the other hand, it does not significantly impact the throughput;
only the transaction verification delay is affected.
We refer the reader to~\cite[Chapter 5]{checo} for additional analysis of the effect of the number of facilitators as well as other experimental results.

### 2017-08-27 paper/s6-conclusion.tex
Grammar fixes etc.

We introduced an application neutral blockchain system which we call \textsc{Checo}.
The checkpoint block is added to the existing TrustChain data structure for use in our consensus protocol.
The round based consensus protocol uses ACS as a building block to reach consensus on checkpoint blocks.
The consensus result lets nodes elect new facilitators and create new checkpoint blocks.
To make transactions, nodes use the transaction protocol,
which is adapted from an existing work called True Halves.
Finally, we introduce a validation protocol which ensures that if an agreed fragment for some transaction exists,
then nodes reach agreement on the validity of that transaction.
The novelty of the validation protocol is that it uses point-to-point communication,
i.e. nodes only validate the transactions of interest,
this enables our horizontal scalability property.

We achieve the properties described in the Problem Description (\Cref{sec:description}).
Namely, our protocol achieves agreement and validity as we argued in~\Cref{sec:correctness-of-validity}.
Further, the horizontal scalability is demonstrated in~\Cref{sec:implementation},
in the ideal case as well as the worst case.
In the future, we hope to apply our system to a concrete application and evaluate its performance.

>>>>

In this work, we described \textsc{Checo}, an application neutral blockchain system with horizontal scalability.
Our novel data structure allows nodes to efficiently store transactions and record state using CP blocks.
The round based consensus protocol uses ACS as a building block to reach consensus on CP blocks.
The consensus result lets nodes elect new facilitators and create new checkpoint blocks.
To make transactions, nodes use the simple and non-blocking transaction protocol.
Finally, we introduce a validation protocol which ensures that if an agreed fragment for some transaction exists,
then nodes reach agreement on the validity of that transaction.
The novelty of \textsc{Checo} is that it decouples consensus and transaction validation,
which enables the desirable horizontal scalability property.

We achieve the properties described in~\Cref{sec:description}.
Namely, our protocol achieves agreement on transactions as we argued in~\Cref{sec:correctness-of-validity}.
Further, the horizontal scalability is demonstrated in~\Cref{sec:implementation},
in the ideal case as well as the worst case.
In the future, we hope to apply our system to a concrete application and evaluate its performance.
